---
title: "trigrams from pound & frost"
output: html_notebook
---

```{r load_libs, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse); library(magrittr); library(stringr); library(tidytext); 
library(gutenbergr); library(stringdist); library(DT)
```

#### Get texts

```{r get_books}
frost <- gutenberg_download(c(3021, 3026, 29345))

frost_trigrams <-
  frost %>%
  slice(c(84:1046,1061:1070,1095:3258,3341:5228)) %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3)

pound <- gutenberg_download(c(23538,40200,41162,51992))

pound_trigrams <- 
  pound %>% 
  slice(c(76:683,734:1783,1946:3566,3861:6274)) %>%
  unnest_tokens(trigram, text, token = "ngrams", n = 3) 
```

#### Find patterns

```{r, echo=TRUE, message=FALSE, warning=FALSE}
str1 <- pound_trigrams %>% select(word = trigram) %>% sample_n(1000) %>% distinct() 
str2 <- frost_trigrams %>% select(word = trigram) %>% sample_n(1000) %>% distinct()  

source("tools/simil.R")

rearrange(str1$word, str2$word) %>% datatable(rownames = F,filter = "top")

```

#### Gleanings

another day thin and over again
the wheel turns the withered tree

war they made of the dead
at worm turning the sun something
the vasty deep that lifted eyes

with the view worth the mortgage
thought to see out of the
evening haze the everything went well


either will there is the sweetest
aye and no and over again

let's to music tell us it
he ran mad like a dream
you will not oh i won't
light athwart the that is what

thus the empire without the birds
not write lest root and violets
the soil meets tall slim trees
our eyes you nodded yes to
the noose was the abyss of
the little streams time tell me
would have thrown woods to northward
vast waters flowed time was wasted
singing the stars is the sweetest
candle the stars make it stay

i shall have over all the
the birds of the yard the

sung these things not gathering roses
and unbind the doubt if they
was no glimpse so we climbed
the night nor the literal to

war they made what their names
author of the bare thought of
things are set in the game
he passed from the abyss of
passed in many gaps i mean
their marcescent wings tries once twice
torn torn with storm but why
and yet again cut and begin
reforming sense to man for seeing
the day through the earth crumbs
of departed locusts of devoted souls
lone might gainst something strange i
in bower in a cobweb diamond
day comes on a cobweb diamond
watch and maketh a thousand times
tasting the grass against their wall
the companions of the ceiling as
tongue and temper enough i wonder
awake and in pale and dim
the end of the faded earth
know not how bow you know
is not if it was snowing
lead heavy rest above the forest
upon the petals out the self
as beneath half a stone hear
and the passion a hole i
gleaming in patches meaning of it
but i forget bit of everything
to a sea to learn baseball
upon the porcelain, upon the trail
the same and the swale in
books and weary look and try
the white hart the literal to
old and here holy land where
sung these things the sun something
in the blue finding the battle
the earth in there he is
in their hearts in another star
the wave in the pew and
lone might gainst something strange i
we are old we have to
the dark we the orchard white
