---
title: "On Walls"
output: html_notebook
---

```{r}
library(tidyverse); library(magrittr); library(stringr); library(tidytext); library(stringdist); library(gutenbergr)
```

Get sources on ancient cities:

```{r}

ancient_town <-
  gutenberg_download(14189, meta_fields = c("title","author"),strip = T) %>%
  # Remove header and footer matter
  slice(250:3823) %>%
  # Number lines for reference
  mutate(line = row_number()) 

ancient_city_1 <-
  gutenberg_download(40860, meta_fields = c("title","author"),strip = T) %>%
  # Remove header and footer matter
  slice(170:14960) %>%
  # Number lines for reference
  mutate(line = row_number()) 

ancient_city_2 <-
  gutenberg_download(44449, meta_fields = c("title","author"),strip = T) %>%
  # Remove header and footer matter
  slice(134:16680) %>%
  # Number lines for reference
  mutate(line = row_number()) 

ancient_walls <- bind_rows(ancient_town,ancient_city_1,ancient_city_2)

find <- c("wall","boundar","door","entrance","border","enclos","divid",
          "barrier","partition")

unnest_walls <- 
  ancient_walls %>%
  unnest_tokens(words,text,"ngrams",n = 10) %>%
  mutate(
    matches = grepl(
      pattern = paste0("^",paste(find, collapse = " |^")), words
    )
  ) %>%
  filter(matches == T)

```

Get Strabo's *"The Inhabited World"*

```{r get_strabo}
# The Inhabited World according to Strabo (vol 1) 
strabo_1 <- 
  readLines("https://archive.org/stream/in.gov.ignca.2913/2913_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  slice(2476:24482) %>%
  mutate(
    title = "The Inhabited World",
    author = "Strabo"
  )

# The Inhabited World according to Strabo (vol 2) 
strabo_2 <- 
  readLines("https://archive.org/stream/in.gov.ignca.2914/2914_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  slice(700:20952) %>%
  mutate(
    title = "The Inhabited World",
    author = "Strabo"
  )

# The Inhabited World according to Strabo (vol 3) 
strabo_3 <- 
  readLines("https://archive.org/stream/in.gov.ignca.2915/2915_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  slice(719:18236) %>%
  mutate(
    title = "The Inhabited World",
    author = "Strabo"
  )

# The Inhabited World according to Strabo (vol 4) 
strabo_4 <- 
  readLines("https://archive.org/stream/in.ernet.dli.2015.57228/2015.57228.Geography-Of-Strabo-Vol-4_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  slice(686:21746) %>%
  mutate(
    title = "The Inhabited World",
    author = "Strabo"
  )

# The Inhabited World according to Strabo (vol 5) 
strabo_5 <- 
  readLines("https://archive.org/stream/in.gov.ignca.2917/2917_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  slice(680:24503) %>%
  mutate(
    title = "The Inhabited World",
    author = "Strabo"
  )

# The Inhabited World according to Strabo (vol 6) 
strabo_6 <- 
  readLines("https://archive.org/stream/in.ernet.dli.2015.57230/2015.57230.Geography-Of-Strabo-Vol-6_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  slice(651:18006) %>%
  mutate(
    title = "The Inhabited World",
    author = "Strabo"
  )

# The Inhabited World according to Strabo (vol 7) 
strabo_7 <- 
  readLines("https://archive.org/stream/in.ernet.dli.2015.57231/2015.57231.Geography-Of-Strabo-Vol-7_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  slice(677:17413) %>%
  mutate(
    title = "The Inhabited World",
    author = "Strabo"
  )

# The Inhabited World according to Strabo (vol 6) 
strabo_8 <- 
  readLines("https://archive.org/stream/in.ernet.dli.2015.57232/2015.57232.Geography-Of-Strabo-Vol-8_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  slice(626:10453) %>%
  mutate(
    title = "The Inhabited World",
    author = "Strabo"
  )

inhabited_world <-
strabo_1 %>%
  bind_rows(strabo_2,strabo_3,strabo_4,strabo_5,strabo_6,strabo_7,strabo_8) %>%
  mutate(
    text = str_trim(text),
    # Replace numbers and spaces with ""
    text = str_replace(text,"^[\\d\\s]+$",""),
    text = str_replace_all(text,"[[:punct:]]|Â|^|>","")
  ) %>%
  filter(text != "" & text != "STRABO") 

rm(strabo_1); rm(strabo_2); rm(strabo_3); rm(strabo_4)
rm(strabo_5); rm(strabo_6); rm(strabo_7); rm(strabo_8)

```

Get recent news articles using the word *wall* from the NYT and The Guardian.

```{r nyt_query}
library(rtimes)
# Sys.setenv(NYTIMES_AS_KEY = "d62e45fd0479489faa7cb595e801aa08")
x <- as_search(
  q = "wall",
  begin_date = "20160101", 
  end_date = "20171112",
  all_results = T)

tst <- x$data
```

```{r guardian_query}
# Guardian API limits the date range of records, so use a loop to call multiple
# consecutive months

multi_guardian <- 
  function(query,section,from,n_mos,key) {
    library(GuardianR); library(lubridate); library(tidyverse)
    results <- data.frame()
    from <- ymd(from)
    for (i in 1:n_mos) {
      month_result <- 
      get_guardian(
        query,
        section = section,
        from.date = as.character(from),
        to.date = as.character(ceiling_date(from, unit = "month")),
        api.key = key
      )
      from <- from %m+% months(1)
      results <- bind_rows(results,month_result)
    }
    return(results)
  }

modern_walls <-
multi_guardian(
  query = "wall",
  section = "world",
  from = "2016-01-01",
  n_mos = 12,
  key = "4fccf9a1-64e9-407b-ad42-29e28bc9d7ce"
)

# Remove html tags from text
library(htmltools)
tst <- modern_walls %>%
  mutate(
    # text = html_text(read_html(body)),
    text = htmlEscape(body),
    text = gsub("*\\>.*?\\<*", " ", text)
  ) %>%
  separate_rows(text, sep = ". ")


```

Find patterns

```{r}
wall_words <- c("wall","walls","border","borders","boundary","boundaries",
                "gate","gates","door","doors","divide","divides",
                "security","secure","outside","inside","haven",
                "harbor","harbour","key","keys","hinge","hinges")

unnest_world <- 
  inhabited_world %>%
  unnest_tokens(words,text,"ngrams",n = 5) %>%
  mutate(
    make = grepl(
      pattern = paste0("^",paste(wall_words, collapse = " |^")), words
    )
  ) %>%
  filter(make == T)

```


* * * * * 

A door is a way of holding in or out blessings or curses.

On the inside of the wall is starvation.
On the outside is exposure.
A door modulates, a song of economy.

The ratio of opening and closing is temperance.
IC XC says: "I have put before you an open door, which no one is able to shut."
The Liturgy says: "The doors, (close) the doors.  Let us attend."

A mountaintop is a million entrances in all directions.
One must scale the wall to arrive there each moment.

Door :: 'porta', from 'portare', to bring, which has a sense of openness, of generosity,
of shared worlds (though distinct, enriching one another)

Walls with banners, slogans, announcing who we wish to be.
Regulate, make space for peace within, if peace is uniformity.

Have I run this far to build a wall of air around me?

To rebuild the borders of my contested life?

In the midst of the door is a ring.  Marry the path.

cf. Harrison: at Athenian weddings, a boy carried a winnowing fan, saying:
"Bad have I fled, better have I found."  A winnowing of paths.

In some of the oldest extant cities, the buildings have no doors.
Çatalhöyük, for example, had no public buildings but only dwellings - like caves laid horizontal,
open to the sky instead of to the land.

What a revolution the public square must have been, the piazza/plein.  A place where it was safe to be with others, enclosed but open.

In America, we have reverted to doorless homes.  Our caves open only to the transmissions of waves.


The Greek for 'initiation' τελέω :: 'fulfillment'