---
title: "The Construction of the Heavens"
output: html_notebook
---

```{r load_libs, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse); library(magrittr); library(stringr); library(tidytext); library(stringdist)
```

from *[Philosophical transactions of the Royal Society](https://archive.org/details/philosophicaltransactions)* 

```{r get_books, message=FALSE, warning=FALSE, include=FALSE}

# On the Construction of the Heavens. By William Herschel, Esq. 
# Philosophical Transactions of the Royal Society of London (1776-1886).
construct_heaven <- 
  readLines("https://ia600504.us.archive.org/12/items/philtrans02233147/02233147_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  mutate(
    title = "On the Construction of the Heavens",
    author = "Herschel, William"
  )

# On the Nature and Construction of the Sun and Fixed Stars. By William Herschel
# Philosophical Transactions of the Royal Society of London (1776-1886).
construct_sun <- 
  readLines("https://ia800500.us.archive.org/16/items/philtrans08894694/08894694_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  mutate(
    title = "On the Nature and Construction of the Sun and Fixed Stars",
    author = "Herschel, William"
  )

# Catalogue of a Second Thousand of New Nebulae and Clusters of Stars; 
# With a Few Introductory Remarks on the Construction of the Heavens. 
# By William Herschel, W Philosophical Transactions of the Royal Society of London (1789).
construct_nebulae <- 
  readLines("https://ia800701.us.archive.org/11/items/philtrans08124673/08124673_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  mutate(
    title = "Catalogue of a Second Thousand of New Nebulae and Clusters of Stars With a Few Introductory Remarks on the Construction of the Heavens",
    author = "Herschel, William"
  )

construct_heaven %<>%
  bind_rows(construct_sun) %>%
  bind_rows(construct_nebulae) %>%
  mutate(
    text = str_trim(text),
    # Replace numbers and spaces with ""
    text = str_replace(text,"^[\\d\\s]+$",""),
    text = str_replace_all(text,"[[:punct:]]|Â|^|>","")
  ) %>%
  filter(text != "") %>%
  filter(nchar(text) > 10)

rm(construct_sun); rm(construct_nebulae)

```

from *[the Endeavor Journals of Joseph Banks](http://www2.sl.nsw.gov.au/banks/series_03/03_view.cfm)*

```{r endeavor, message=FALSE, warning=FALSE, include=FALSE}

temp <- tempfile()
download.file("http://www2.sl.nsw.gov.au/banks/download/endevtxt.zip",temp)
endeavor <- readLines(unz(temp, "Endeav.txt"))
unlink(temp)
endeavor %<>% as.data.frame()

```

```{r find_patterns}

make_verbs <- c("construct","make","measure","align","destroy","move","rest",
                "build","add","support","bring","develop","extend","form",
                "render","trace","draw","place","sew","stitch")

unnest_heavens <- 
  construct_heaven %>%
  unnest_tokens(words,text,"ngrams",n = 5) %>%
  mutate(
    prep = grepl(
      pattern = paste0("^",paste(prepositions$word, collapse = " |^")), words
    ),
    make = grepl(
      pattern = paste0("^",paste(make_verbs, collapse = " |^")), words
    )
  ) %>%
  filter(prep == T | make == T)


```

Make some use of this.
In this grand chemical, under the shape of dark
trace the operations

of the shining fluid added by the sun upon 
bodies  to which I have 
joined to be divided into two.

(Draw upon myself without 
attempting to draw to be perceived)

Form what has been said 
from analogy for the illumination 
which remains in this paper 
of light and luminous vapours,
of these appearances I carefully

  build worlds of our own
  as far as we can (*as far from us*)

Above the rough surface as 
the square upon 
the ground the birds form 
the unevenness arising 
  out of a thousand situations - 

In possession of a list
no more than what is sufficiently evident
as the minute parts 

as I can think
    *of explaining it by mountains, by admitting large mountains*
as I have found.

Add the place.  Make it almost improbable.
Place *now* and *then*.
Place *I can only give* on *I need not fear*.

Form, confining around 
him, the whole universe
as vivid the diameters - to discover 

the places where, near 
the margin, we form 
an opening to the naked about.

Extend equally to them all as one 
full grown plant of a crookedly branching 
nebula that would point about 
a center or about 
                    all the spots

make them mere useless 
brilliant for the dark ground
about the dark part
against the moon's being

                        *as its satellite we pass*

As I decompose in the suit drawn pretty of stars
given to it I see 
by some agitation or other in a row a beautiful
                      
as difficultly resolvable
                          above construction 




```{r leftovers}
# after all we can hardly
# into a pretty narrow compass.
# 
# rest about all the spots
# 
# of the landscape are situated
# on the surface of
# of the sun we shall
# 
# from the limb was the
# of the shelving side instead
# to the edge of the
# below the surface of the
# of which we rarely see
# 
# on the moon the unenlightened
# in the edipse of the
# 
# as i approached the milky
# by a volcanic explosion violently
# on its return would gradually
# in diameter which is equal
# 
# up the vacancy and thus
# 
# from them when all the
# 
# with regard to the physical
# with materials for examining
# 
# as nature never exposes
# 
# as could possibly be crowded
# to express in the shortest
# 
# of such fluids 
# 
# within a fphere drawn round
# on our earth the heat
# near to an extinction of
# of plants or animals in
# from the generation of clouds
# 
# 
# 
# next section with one in
# 
# 
#  or colourlefs
# 
# over with whitish and unequally
# for the purposes of animal
# 
# as a cone
# under which we have
# 
# as pretty closely scattered fmall
# from a point not lefs
# 
# 
# to render this point
# of instruction our clouds are
# about his little globe that
# 
# 
# 
# throughout the whole the laws
# of the unevenness of the
# 
#  without the
# make a detached link on an ifland unlefs 
# 
# for instance which my sister
# 
# 
# about 2 minutes about 48 extent about 30 or 40 degrees about 60 or 70 generally about 27 long and in
# 
# form this again we reft
# 
# render this point
# draw additional
# 
# add that the idea of
# extend the weight of my
# 
# 
# add obfervation to obfervation 
# 
# form the letter s 
# form a cross
# 
# make this appear 
# trace the caufe 
# 
# bring some of that
# 
# bring on a subdivision like the shrivelled elevations upon
# support the ideas
# support these stars
# bring down the lustre to be opaque masses
```