---
title: "c o s o m o s"
output: html_notebook
---

```{r load_libs, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse);library(magrittr);library(stringr);library(tidytext);library(stringdist);library(gutenbergr)
```

```{r read_humboldt, message=FALSE, warning=FALSE, include=FALSE}

cosmos_vol_1 <- 
  gutenberg_download(14565,meta_fields = c("title","author"),strip = T) %>%
  mutate(
    title = "Cosmos: Sketch of a Physical Description of the Universe",
    volume = "1",
    author = "von Humboldt, Alexander"
  ) %>%
  select(-gutenberg_id) %>%
  # Remove header and footer matter
  slice(962:17497) %>%
  # Number lines for reference
  mutate(line = row_number()) 

cosmos_vol_2 <- 
  readLines("https://ia800206.us.archive.org/8/items/cosmosvolume00humbgoog/cosmosvolume00humbgoog_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  mutate(
    title = "Cosmos: Sketch of a Physical Description of the Universe",
    volume = "2",
    author = "von Humboldt, Alexander"
  ) %>%
  # Remove header and footer matter
  slice(310:20421) %>%
  # Number lines for reference
  mutate(line = row_number()) 

cosmos_vol_3 <- 
  readLines("https://ia802700.us.archive.org/24/items/cosmosasketchap01humbgoog/cosmosasketchap01humbgoog_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  mutate(
    title = "Cosmos: Sketch of a Physical Description of the Universe",
    volume = "3",
    author = "von Humboldt, Alexander"
  ) %>%
  # Remove header and footer matter
  slice(1287:15543) %>%
  # Number lines for reference
  mutate(line = row_number())

cosmos_vol_4 <- 
  readLines("https://ia800206.us.archive.org/8/items/cu31924073049839/cu31924073049839_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  mutate(
    title = "Cosmos: Sketch of a Physical Description of the Universe",
    volume = "4",
    author = "von Humboldt, Alexander"
  ) %>%
  # Remove header and footer matter
  slice(755:16985) %>%
  # Number lines for reference
  mutate(line = row_number())

cosmos_vol_5 <- 
  readLines("https://ia800203.us.archive.org/27/items/cu31924073049847/cu31924073049847_djvu.txt",skipNul = T) %>% 
  as.data.frame() %>%
  rename_all(funs(gsub(.)), pattern = ".", replacement = "text") %>%
  mutate(
    title = "Cosmos: Sketch of a Physical Description of the Universe",
    volume = "5",
    author = "von Humboldt, Alexander"
  ) %>%
  # Remove header and footer matter
  slice(272:25651) %>%
  # Number lines for reference
  mutate(line = row_number())

cosmos <- cosmos_vol_1 %>% bind_rows(cosmos_vol_2,cosmos_vol_3,cosmos_vol_4,cosmos_vol_5)

rm(cosmos_vol_1);rm(cosmos_vol_2);rm(cosmos_vol_3);rm(cosmos_vol_4);rm(cosmos_vol_5)

```

```{r get_univowels, message=FALSE, warning=FALSE, include=FALSE}

n_vowel <- 2

unnest_cosmos <- 
  cosmos %>%
  unnest_tokens(word, text, "ngrams", n = 1) %>% 
  mutate(
    word = as.character(word),
    a = str_count(word,"a"),
    e = str_count(word,"e"),
    i = str_count(word,"i"),
    o = str_count(word,"o"),
    u = str_count(word,"u"),
    y = str_count(word,"y")
  ) %>%
  mutate(
    single_vowel = 
      a > n_vowel & e == 0 & i == 0 & o == 0 & u == 0 & y == 0 
      | a == 0 & e > n_vowel & i == 0 & o == 0 & u == 0 & y == 0 
      | a == 0 & e == 0 & i > n_vowel & o == 0 & u == 0 & y == 0 
      | a == 0 & e == 0 & i == 0 & o > n_vowel & u == 0 & y == 0 
      | a == 0 & e == 0 & i == 0 & o == 0 & u > n_vowel & y == 0
      | a == 0 & e == 0 & i == 0 & o == 0 & u == 0 & y > n_vowel 
  ) %>%
  # Tag words with length > 1 and only one of the vowel using a trailing asterisk
  mutate(
    word = ifelse(
      single_vowel == T & length(word) > 1, 
      paste0(word,"*"), 
      word
    )
  ) %>%
  ungroup() %>%
  select(title:word) %>%
  filter(is.na(word) == F) %>%
  mutate(
    tag = str_detect(word,"\\*"),
    running = cumsum(as.numeric(tag))
  ) %>%
  group_by(running) %>%
  mutate(
    word_n = row_number()
  ) 

lead_10 <- unnest_cosmos %>% top_n(-10,word_n) %>% filter(running != 0) 

# Count of 11 includes tagged word
lag_10 <-  unnest_cosmos %>% top_n(11,word_n) %>% ungroup() %>% filter(running != max(running))

# Define function to count distinct letters
count_distinct_chars <- function(x) map_int(map(x, function(x) unique(strsplit(x, "")[[1]])), length)

cosmos_vowel_lines <- 
  lead_10 %>% 
  bind_rows(lag_10) %>%
  ungroup() %>%
  arrange(running,word_n) %>%
  mutate(group = rep(1:21, length.out = nrow(.))) %>%
  mutate(
    tag = group == 1,
    running = cumsum(as.numeric(tag))
  ) %>%
  group_by(title,author,volume,running) %>%
  select(title,author,volume,running,word) %>%
  distinct() %>%
  # Reassemble unnested data into lines
  nest(word) %>%
  mutate(
    text = map(data, unlist), 
    text = map_chr(text, paste, collapse = " ")
  ) %>%
  select(title:volume,text) %>%
  mutate(
    distinct_letters = count_distinct_chars(text),
    all_letters = nchar(text),
    ratio_distinct = round(distinct_letters/all_letters*100, digits = 1)
  ) %>%
  select(-distinct_letters,-all_letters) %>%
  arrange(ratio_distinct)

rm(lead_10);rm(lag_10);rm(unnest_cosmos)

```

Need to:

- determine additional criteria for filtering (related to content/topic)

Gleanings:

involuntarily associate themselves* with historical
our minds the extinction of suddenly resplendent* stars in cassiopeia cygnus and serpentarius
cause which has hitherto rendered* terrestrial phenomena less amenable
being drawn between* the small
the intimate relation between* light heat electricity
with an elevation elsewhere* as for instance
resting place of glorious colonos* where the melodious nightingale
lines which in older systems represent* arbitrarily and ungracefully horizontally ranged
inclosed in larger and deeper* fissures when atmosphere possessed
an intermediate character situated between* the northern and southern

```{r subset_lines}

cosmos_vowel_lines$text
  
```

