---
title: "Metamorphoses"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse);library(qdapDictionaries)
source("../tools/transform/transform_cloudmorph.R")
```

```{r eval=FALSE, include=FALSE}
clouds <- morph("clouds"); bough <- morph("bough")

rm(list = c("clouds","bough","garbage"))
```

clouds	clours	colours	colors	dolors
clouds	flouds	flouts	floats	flats
bough	rough	rouge	rouse	house
bough	rough	rouge	route	rouse
bough	rough	rouge	route	rote
bough	tough	touch	torch	torah
bough	boughs bought	ought	sought
bough	boughs	bought	brought	drought
inform unform uniform luniform
inform enform enfort effort

```{r}

# inform, cling, cohere, human

x <- morph("inform")

x %>%
  group_by_at(vars(word_0:word_2)) %>%
  summarize(n_words = n_distinct(word)) %>%
  View()

x %>%
  filter(
    word_1 %in% c("enform"),
    word_2 %in% c("enfort")
  ) %>%
  group_by_at(vars(word_0:word_3)) %>%
  # summarize(n_words = n_distinct(word)) %>%
  View()

```


time-lapse of clouds across the mind
changing by erosion or accretion

Snow, lavender and gold

Does the meaning of a stone change after the wave?
The meaning of a cloud when the celebrant wind tears it?


Word as raw element, morphs slightly.
Sense tenuously coheres.  It dissipates with the smallest tick, a letter.

One finds a word.  Leaves it in the dictionary, where it changes.
A word is said.  Years move.  It changes.
Between a book's covers.   Within the folds of the mind.  

We hear a word, and it means all of its almost twins at once.
As possible futures, hallways it could have been and is.

There is one universe, not millions.  
There are infinite universes, each only a moment long.  
A million sequential, momentary universes.

We live across them.

---

Experiments:

lace
